---
title: "UTK Publication Analysis"
author: "Alexander Harriman"
date: "2024-10-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load Packages

```{r}
library(dplyr)
library(tidyverse)
library(gt)
library(ggplot2)
library(readxl)
library(magrittr)
library(ggpmisc)
library(bbplot)
```




# Load Data

```{r, warning = FALSE}
rawData <- read_excel('UTK Publication Data.xlsx')
```


# Filter Data to Significant Information Only



```{r}
filteredData <- rawData |>
  filter(`Publication Year` >= 1973 &
           `Publication Year` <= 2024 &
           'Article' %in% `Document Type`)

filteredData
```


# Publications by Month and Year


```{r}
# Create month-year date column

dateData <- filteredData |>
  mutate(Month = substr(`Publication Date`, 1, 3)) |>
  mutate(Date = case_when(
    Month == 'JAN' ~ as.Date(paste0(as.character(`Publication Year`), '-01-01')),
    Month == 'FEB' ~ as.Date(paste0(as.character(`Publication Year`), '-02-01')),    
    Month == 'MAR' ~ as.Date(paste0(as.character(`Publication Year`), '-03-01')),
    Month == 'APR' ~ as.Date(paste0(as.character(`Publication Year`), '-04-01')),
    Month == 'MAY' ~ as.Date(paste0(as.character(`Publication Year`), '-05-01')),
    Month == 'JUN' ~ as.Date(paste0(as.character(`Publication Year`), '-06-01')),
    Month == 'JUL' ~ as.Date(paste0(as.character(`Publication Year`), '-07-01')),
    Month == 'AUG' ~ as.Date(paste0(as.character(`Publication Year`), '-08-01')),
    Month == 'SEP' ~ as.Date(paste0(as.character(`Publication Year`), '-09-01')),
    Month == 'OCT' ~ as.Date(paste0(as.character(`Publication Year`), '-10-01')),
    Month == 'NOV' ~ as.Date(paste0(as.character(`Publication Year`), '-11-01')),
    Month == 'DEC' ~ as.Date(paste0(as.character(`Publication Year`), '-12-01')),
    .default = NA
  ))
```




# Publications by Number of Co-Authors

```{r}
numAuthors <- vector()
for(i in 1:dim(dateData)[1]){
  authorString <- str_split_1(dateData$`Author Full Names`[i], ';')
  numAuthors[i] <- length(authorString)
}

allAuthor <- cbind(dateData, numAuthors)
```




# Citation and Usage Numbers by Number of Authors


```{r}
authorUsage <- allAuthor |>
  mutate(authorClass = case_when(
    numAuthors < 4 ~ 'Low',
    numAuthors >= 4 & numAuthors < 14 ~ 'Med',
    numAuthors >= 14 ~ 'High'
  ),
  usagePerYear = `Since 2013 Usage Count` / (2025 - `Publication Year`)) |>
  group_by(authorClass) |>
  summarise(publications = n(),
            averageUsageRecent = mean(`180 Day Usage Count`),
            averageUsagePerYear = mean(usagePerYear),
            averageCitations = mean(`Times Cited, All Databases`))
```






## Trends in Usage per Year


```{r}
authorUsageWithYear <- allAuthor |>
  filter(`Publication Year` >= 2013 & `Publication Year` != 2024) |>
  mutate(authorClass = factor(case_when(
    numAuthors < 4 ~ '1-3',
    numAuthors >= 4 & numAuthors < 14 ~ '4-14',
    numAuthors >= 14 ~ '15+'
  )),
  usagePerYear = `Since 2013 Usage Count` / (2025 - `Publication Year`)) |>
  group_by(authorClass, `Publication Year`) |>
  summarise(publications = n(),
            averageUsageRecent = mean(`180 Day Usage Count`),
            averageUsagePerYear = mean(usagePerYear),
            averageCitations = mean(`Times Cited, All Databases`)) |>
  arrange(factor(authorClass, levels = c('15+', '4-14', '1-3')))
```




```{r}
authorUsageWithYear |>
  mutate(`# Authors` = factor(authorClass, levels = c('15+', '4-14', '1-3'))) |>
  ggplot(aes(x = `Publication Year`, y = publications, colour = `# Authors`)) +
  geom_line(size = 0.8, aes(linetype = `# Authors`)) +
  geom_point(size = 2) +
  ggtitle('Number of Articles per Year by Author Count') +
  xlab('Year') +
  ylab('# Articles') +
  labs(fill = '# Authors') +
  scale_colour_manual(values = c('#FF8200', '#03AC13', '#051094')) +
  scale_x_continuous(breaks = 2013:2024) +
  theme(plot.title = element_text(size = 20,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 14,
                                   color = '#4b4b4b',
                                   face = 'bold')) +
  theme(axis.title.x = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(legend.title = element_text(color = '#4b4b4b',
                                    face = 'bold')) +
  theme(legend.position = 'top')


ggsave('Number of Articles per Year by Author Count.png', width = 8, height = 4, units = 'in', dpi = 300)
```





# Publication by Publisher


```{r}
publisherInfo <- dateData |>
  filter(`Publication Year` >= 2013) |>
  group_by(Publisher) |>
  summarise(publications = n()) |>
  arrange(desc(publications))
```



```{r}
bigList <- publisherInfo |>
  filter(publications > 100)

bigList <- bigList$Publisher
```



## Group Publishers Together


```{r, warning = FALSE}
dateData2 <- dateData |>
  filter(`Publication Year` >= 2013)

publisherGroup <- vector()
for(i in 1:dim(dateData2)){
  Group <- case_when(
    str_detect(dateData2$Publisher[i], 'UNIV') == TRUE ~ 'University Press',
    str_detect(dateData2$Publisher[i], 'ELSEVIER') == TRUE ~ 'Elsevier',
    str_detect(dateData2$Publisher[i], 'WILEY') == TRUE ~ 'Wiley',
    str_detect(dateData2$Publisher[i], 'SAGE') == TRUE ~ 'Sage',
    str_detect(dateData2$Publisher[i], 'SPRINGER') == TRUE ~ 'Springer',
    str_detect(dateData2$Publisher[i], 'TAYLOR') == TRUE ~ 'T&F',
    .default = 'Other'
  )
  finalGroup <- case_when(
    Group == 'University Press' ~ 'University Press',
    Group != 'Other' & Group != 'American Society' & Group != 'University Press' ~ 'Big 5',
    Group == 'Other'  & dateData2$Publisher[i] %in% bigList ~ 'Medium (>100 Pubs)',
    Group == 'Other' & !dateData2$Publisher[i] %in% bigList ~ 'Small (<100 Pubs)',
    .default = NA
  )
  publisherGroup[i] <- finalGroup
}  

publisherData <- cbind(dateData2, publisherGroup)
```




```{r}
publicationYearData <- publisherData |>
  group_by(publisherGroup, `Publication Year`) |>
  summarise(n = n()) |>
  arrange(publisherGroup, `Publication Year`) |>
  mutate(publisherGroup = factor(publisherGroup, levels = c('Big 5', 'Medium (>100 Pubs)', 'Small (<100 Pubs)', 'University Press')))
```


```{r}
ggplot(publicationYearData, aes(x = `Publication Year`, y = n, colour = publisherGroup)) +
  geom_point(size = 2) +
  geom_line(size = 0.8, aes(linetype = publisherGroup)) +
  ggtitle('Where Researchers Publish In') +
  xlab('Year') +
  ylab('# Articles') +
  labs(colour = 'Publisher Type',
       linetype = 'Publisher Type') +
  scale_x_continuous(breaks = 2013:2024) +
  theme(plot.title = element_text(size = 20,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 12,
                                   color = '#4b4b4b',
                                   face = 'bold')) +
  theme(axis.title.x = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(legend.title = element_blank()) +
  labs(caption = 'Big 5 Publishers: Elsevier, Wiley, Sage, Springer, Taylor & Francis.') +
  theme(plot.caption = element_text(size = 12,
                                    color = '#4b4b4b')) +
  theme(legend.position = 'top') +
  scale_colour_manual(values = c('#2271B2', '#F748A5', '#E69F00', '#359B73'))


ggsave('Where Researchers Publish In.png', width = 8, height = 4, units = 'in', dpi = 300)
```


## Web of Science Impact Factor

Using the top 600 Journal Impact Factors from each year from 2014-23.



```{r}
allWOS <- read.csv('Top WoS Journals by Impact Factor.csv')

colnames(allWOS) <- c('Publisher', 'ISSN', 'eISSN', 'JIF', 'Publication Year')
```


```{r}
publisherData$Date <- NULL
```


```{r, warning = FALSE}
wosCombined <- left_join(publisherData, allWOS, by = c('eISSN', 'Publication Year', 'Publisher', 'ISSN')) |>
  filter(is.na(JIF) == FALSE) |>
  distinct()
```




# Group Publications by Journal Factor


```{r}
test <- wosCombined |>
  filter(`Publication Year` >= 2014 & `Publication Year` <= 2023) |>
  group_by(round(JIF, 0)) |>
  summarise(n = n())

test
```


With a median of slightly above 5, anything below 5 will be low impact factor, while anything above 5 will be high impact factor.



## Impact Factor Group by Year

```{r}
jifClean3 <- wosCombined |>
  mutate(groupJIF = case_when(
    JIF < 5 ~ 'Low',
    JIF >= 5 ~ 'High'
  ))

yearCount <- jifClean3 |>
  group_by(`Publication Year`, groupJIF) |>
  summarise(n = n())
```


## Impact Factor Group by Publication Type


```{r}
publisherBreakdown3 <- jifClean3 |>
  filter(is.na(JIF) == FALSE) |>
  group_by(publisherGroup) |>
  summarise(n = n(),
            meanJIF = round(mean(JIF),1)) |>
  arrange(desc(meanJIF)) |>
  select(publisherGroup, meanJIF) |>
  mutate(publisherGroup = factor(publisherGroup, levels = c('Big 5', 'Medium (>100 Pubs)', 'Small (<100 Pubs)', 'University Press')))
```

```{r}
usageJIFPlot <- ggplot(publisherBreakdown3, aes(x = publisherGroup, y = meanJIF, fill = publisherGroup)) +
  geom_col() +
  ggtitle('Mean JIF by Publisher Type') +
  xlab('Publisher Type') +
  ylab('Mean JIF') +  
  theme(plot.title = element_text(size = 20,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 10,
                                   color = '#4b4b4b',
                                   face = 'bold')) +
  theme(axis.title.x = element_text(size = 14,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 14,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(legend.title = element_blank()) +
  
  labs(caption = 'Based on Top 600 Journals by JIF Each Year, 2014-2023') +
  geom_text(aes(label = meanJIF), vjust = -0.5) +
  expand_limits(y = 8) +
  scale_fill_manual(values = c('#2271B2', '#F748A5', '#E69F00', '#359B73'))

usageJIFPlot

ggsave('Mean JIF by Publisher Type.png', width = 8, height = 4, units = 'in', dpi = 300)
```



# InCites Data from U.S. Universities



```{r}
allUni <- read_csv('InCites Data Across the USA.csv')
```



## Publication Trends by University: 10-Year Averages



```{r}
uniSummaries <- allUni |>
  group_by(Name, `State or Province`) |>
  summarise(Years = n(),
            Publications = sum(`Web of Science Documents`),
            PublicationsCorresponding = sum(`Corresponding Author (2008-2024)`),
            CollabsDomestic = sum(`Domestic Collaborations`),
            CollabsInternational = sum(`International Collaborations`),
            Citations = sum(`Times Cited without Self-Citations`),
            OAPubs = sum(`Gold Documents`),
            HIndex = sum(`H-Index without Self-Citations`)) |>
  mutate(AvgPubs = Publications / Years,
         AvgIndex = HIndex / Years,
         AvgCites = Citations / Years,
         OARate = 100.0*(OAPubs / Publications)) |>
  filter(Years == 10) |>
  arrange(desc(AvgIndex))
```


## Publication Trends by University: Yearly Averages



```{r}
uniByYear <- allUni |>
  group_by(Name, `State or Province`, Year) |>
  summarise(Publications = sum(`Web of Science Documents`),
            PublicationsCorresponding = sum(`Corresponding Author (2008-2024)`),
            CollabsDomestic = sum(`Domestic Collaborations`),
            CollabsInternational = sum(`International Collaborations`),
            Citations = sum(`Times Cited without Self-Citations`),
            OAPubs = sum(`Gold Documents`),
            HIndex = sum(`H-Index without Self-Citations`)) |>
  mutate(OARate = 100.0*(OAPubs / Publications)) |>
  arrange(desc(HIndex))
```


# Trends at the Top Southern Universities


```{r}
topSouth <- uniSummaries |>
  filter(`State or Province` == 'TENNESSEE, USA' |
           `State or Province` == 'GEORGIA, USA' |
           `State or Province` == 'ALABAMA, USA' |
           `State or Province` == 'KENTUCKY, USA' |
           `State or Province` == 'VIRGINIA, USA' |
           `State or Province` == 'NORTH CAROLINA, USA' |
           `State or Province` == 'SOUTH CAROLINA, USA' |
           `State or Province` == 'FLORIDA, USA' |
           `State or Province` == 'MISSISSIPPI, USA' |
           `State or Province` == 'LOUISIANA, USA' |
           `State or Province` == 'TEXAS, USA' |
           `State or Province` == 'OKLAHOMA, USA' |
           `State or Province` == 'ARKANSAS, USA') |>
  arrange(desc(AvgIndex)) |>
  head(n = 25)
```


```{r}
topSouth2 <- uniByYear |>
  filter(Name %in% c('Duke University',
                     'University of North Carolina Chapel Hill',
                     'Vanderbilt University',
                     'University of Texas Austin',
                     'University of Florida',
                     'Georgia Institute of Technology',
                     'University of Virginia',
                     'Texas A&M University College Station',
                     'University of Miami',
                     'University of Tennessee Knoxville')) |>
  mutate(Name = case_when(
    Name == 'Duke University' ~ 'Duke',
    Name == 'University of North Carolina Chapel Hill' ~ 'UNC - Chapel Hill',
    Name == 'Vanderbilt University' ~ 'Vanderbilt',
    Name == 'University of Texas Austin' ~ 'Texas - Austin',
    Name == 'University of Florida' ~ 'Florida',
    Name == 'Georgia Institute of Technology' ~ 'Georgia Tech',
    Name == 'University of Virginia' ~ 'Virginia',
    Name == 'Texas A&M University College Station' ~ 'Texas A&M',
    Name == 'University of Miami' ~ 'Miami (FL)',
    Name == 'University of Tennessee Knoxville' ~ 'UT Knoxville'
  )) |>
  mutate(Name = factor(Name, levels = c('Duke',
                                        'Florida',
                                        'UNC - Chapel Hill',
                                        'Vanderbilt',
                                        'Texas - Austin',
                                        'Texas A&M',
                                        'Virginia',
                                        'Miami (FL)',
                                        'Georgia Tech',
                                        'UT Knoxville'
  )))
```


```{r}
ggplot(topSouth2, aes(x = Year, y = Publications, colour = Name)) +
  geom_line(aes(linetype = Name)) +
  ggtitle('Top Southeastern Research Universities') +
  xlab('Year') +
  ylab('# Articles Published') +
  scale_x_continuous(breaks = 2014:2023) +
  theme(plot.title = element_text(size = 18,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 12,
                                   color = '#4b4b4b',
                                   face = 'bold')) +
  theme(axis.title.x = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(legend.title = element_blank()) +
  theme(plot.caption = element_text(size = 10,
                                    color = '#4b4b4b')) +
  scale_colour_manual(values = c('Duke' = '#012169',
                                 'UT Knoxville' = '#FF8200',
                                 'UNC - Chapel Hill' = '#007fae',
                                 'Texas A&M' = '#500000',
                                 'Vanderbilt' = '#CFAE70',
                                 'Florida' = '#6a2a60',
                                 'Texas - Austin' = '#bf5700',
                                 'Georgia Tech' = '#54585a',
                                 'Virginia' = '#ef3f6b',
                                 'Miami (FL)' = '#005030'))

ggsave('Top Southeastern Research Universities.png', width = 7, height = 3.5, units = 'in', dpi = 300)
```

# UT Knoxville Publication Data


```{r}
fullPub <- read_csv('All UTK Publications.csv')
```



```{r, fig.align = 'center', echo = FALSE}
ggplot(fullPub, aes(x = Year, y = Publications, colour = Resource)) +
  geom_line(aes(linetype = Resource), size = 1) +
  geom_point(color = '#4b4b4b', size = 3) +
  ggtitle('Publications at the University of Tennessee') +
  xlab('Year') +
  ylab('# Articles Published') +
  scale_x_continuous(breaks = 2014:2023) +
  expand_limits(y = 0) +
  geom_vline(xintercept = 2021) +
  theme(plot.title = element_text(size = 18,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 12,
                                   face = 'bold',
                                   color = '#4b4b4b')) +
  theme(legend.title = element_text(size = 14,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.x = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(plot.caption = element_text(size = 10,
                                    color = '#4b4b4b')) +
  scale_colour_manual(values = c('Web of Science' = '#5E33BF',
                                 'Scopus' = '#F28500',
                                 'Dimensions' = '#97C997')) +
  theme(legend.position = 'top')

ggsave('Publications at the University of Tennessee.png', width = 8, height = 4, units = 'in', dpi = 300)
```


# How Many Schools Saw a 2019 Rise and a 2022 Fall in Publications


```{r}
highLowUS <- uniByYear |>
  arrange(Name, Year) |>
  mutate(versusLast = case_when(
    Year == 2014 ~ 0,
    Year != 2014 & Publications >= lag(Publications) ~ 1,
    Year != 2014 & Publications < lag(Publications) ~ 0,
    .default = NA))

highLowUS |>
  group_by(versusLast) |>
  summarise(n = n())
```



```{r}
yearToYearRatesUS <- highLowUS |>
  filter(Year >= 2015 & is.na(versusLast) == FALSE) |>
  group_by(Year) |>
  summarise(Schools = n(),
            Improvements = sum(versusLast)) |>
  mutate(ImproveRate = round(100.0*Improvements / Schools, 1)) |>
  arrange(Year)

yearToYearRatesUS
```


```{r}
yearToYearUS <- yearToYearRatesUS |>
  mutate(Region = 'United States')

yearToYearUS
```


# International Publishing Trends




```{r}
allUni <- data.frame()

uniPub <- list.files(pattern = 'Foreign with US', full.names = TRUE)

for(i in 1:length(uniPub)){
  year <- read_excel(uniPub[i]) 
  
  year <- year[,1:11] |>
    mutate(Year = 2013 + i)
  
  allUni <- rbind(allUni, year)
}

allUni <- allUni |>
  mutate(`Country or Region` = case_when(
    `Country or Region` %in% c('ENGLAND', 'SCOTLAND', 'NORTHERN IRELAND', 'WALES') ~ 'UNITED KINGDOM',
    `Country or Region` == 'GERMANY (FED REP GER)' ~ 'GERMANY',
    .default = `Country or Region`
  ))

dim(allUni)
```




## Publication Trends by Nation: 10-Year Averages



```{r}
uniSummaries <- allUni |>
  group_by(`Country or Region`) |>
  summarise(Years = unique(Year),
            Publications = sum(`Web of Science Documents`),
            PublicationsCorresponding = sum(`Corresponding Author (2008-2024)`),
            CollabsDomestic = sum(`Domestic Collaborations`),
            CollabsInternational = sum(`International Collaborations`),
            Citations = sum(`Times Cited without Self-Citations`),
            OAPubs = sum(`Gold Documents`),
            HIndex = sum(`H-Index without Self-Citations`)) |>
  mutate(AvgPubs = Publications / Years,
         AvgIndex = HIndex / Years,
         AvgCites = Citations / Years,
         OARate = 100.0*(OAPubs / Publications)) |>
  arrange(desc(AvgIndex))
```


## Publication Trends by University: Yearly Averages



```{r}
uniByYear <- allUni |>
  group_by(`Country or Region`, Year) |>
  summarise(Publications = sum(`Web of Science Documents`),
            PublicationsCorresponding = sum(`Corresponding Author (2008-2024)`),
            CollabsDomestic = sum(`Domestic Collaborations`),
            CollabsInternational = sum(`International Collaborations`),
            Citations = sum(`Times Cited without Self-Citations`),
            OAPubs = sum(`Gold Documents`),
            HIndex = sum(`H-Index without Self-Citations`)) |>
  mutate(OARate = 100.0*(OAPubs / Publications)) |>
  arrange(desc(HIndex)) |>
  mutate(`Country or Region` = factor(`Country or Region`, levels = c('USA', 'CHINA MAINLAND', 'UNITED KINGDOM', 'GERMANY', 'FRANCE', 'JAPAN', 'SOUTH KOREA')))
```



## Major Publishing Nations Trends


```{r}
ggplot(uniByYear, aes(x = Year, y = Publications, colour = `Country or Region`)) +
  geom_point(size = 2) +
  geom_line(size = 0.8) +
  ggtitle('Publication Trends Around the World') +
  xlab('Year') +
  ylab('# Articles') +
  scale_x_continuous(breaks = 2014:2023) +
  theme(plot.title = element_text(size = 18,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 12,
                                   color = '#4b4b4b',
                                   face = 'bold')) +
  theme(axis.title.x = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(legend.title = element_blank()) +
  theme(plot.caption = element_text(size = 10,
                                    color = '#4b4b4b')) +
  scale_colour_manual(values = c('FRANCE' = '#008000',
                                 'SOUTH KOREA' = '#000000',
                                 'JAPAN' = '#c1328e',
                                 'GERMANY' = '#ffd300',
                                 'UNITED KINGDOM' = '#522D80',
                                 'CHINA MAINLAND' = '#CC0000',
                                 'USA' = '#0A3161'))

ggsave('Publication Trends Around the World.png', width = 8, height = 4, units = 'in', dpi = 300)
```

# How Many Schools Saw a 2019 Rise and a 2022 Fall in Publications - Mainland China

```{r}
uniByYearMLC <- allUni |>
  filter(`Country or Region` == 'CHINA MAINLAND') |>
  group_by(Name, Year) |>
  summarise(Publications = sum(`Web of Science Documents`),
            PublicationsCorresponding = sum(`Corresponding Author (2008-2024)`),
            CollabsDomestic = sum(`Domestic Collaborations`),
            CollabsInternational = sum(`International Collaborations`),
            Citations = sum(`Times Cited without Self-Citations`),
            OAPubs = sum(`Gold Documents`),
            HIndex = sum(`H-Index without Self-Citations`)) |>
  mutate(OARate = 100.0*(OAPubs / Publications)) |>
  arrange(desc(HIndex))
```


```{r}
highLowMLC <- uniByYearMLC |>
  arrange(Name, Year) |>
  mutate(versusLast = case_when(
    Year == 2014 ~ 0,
    Year != 2014 & Publications >= lag(Publications) ~ 1,
    Year != 2014 & Publications < lag(Publications) ~ 0,
    .default = NA))

highLowMLC |>
  group_by(versusLast) |>
  summarise(n = n())
```



```{r}
yearToYearRatesMLC <- highLowMLC |>
  filter(Year >= 2015 & is.na(versusLast) == FALSE) |>
  group_by(Year) |>
  summarise(Schools = n(),
            Improvements = sum(versusLast)) |>
  mutate(ImproveRate = round(100.0*Improvements / Schools, 1)) |>
  arrange(Year)
```



```{r}
yearToYearMLC <- yearToYearRatesMLC |>
  mutate(Region = 'Mainland China')
```


# How Many Schools Saw a 2019 Rise and a 2022 Fall in Publications - Other Nations in Data



```{r}
uniByYearRest <- allUni |>
  filter(`Country or Region` != 'USA' & `Country or Region` != 'CHINA MAINLAND') |>
  group_by(Name, Year) |>
  summarise(Publications = sum(`Web of Science Documents`),
            PublicationsCorresponding = sum(`Corresponding Author (2008-2024)`),
            CollabsDomestic = sum(`Domestic Collaborations`),
            CollabsInternational = sum(`International Collaborations`),
            Citations = sum(`Times Cited without Self-Citations`),
            OAPubs = sum(`Gold Documents`),
            HIndex = sum(`H-Index without Self-Citations`)) |>
  mutate(OARate = 100.0*(OAPubs / Publications)) |>
  arrange(desc(HIndex))
```


```{r}
highLowRest <- uniByYearRest |>
  arrange(Name, Year) |>
  mutate(versusLast = case_when(
    Year == 2014 ~ 0,
    Year != 2014 & Publications >= lag(Publications) ~ 1,
    Year != 2014 & Publications < lag(Publications) ~ 0,
    .default = NA))

highLowRest |>
  group_by(versusLast) |>
  summarise(n = n())
```



```{r}
yearToYearRatesRest <- highLowRest |>
  filter(Year >= 2015 & is.na(versusLast) == FALSE) |>
  group_by(Year) |>
  summarise(Schools = n(),
            Improvements = sum(versusLast)) |>
  mutate(ImproveRate = round(100.0*Improvements / Schools, 1)) |>
  arrange(Year)
```



```{r}
yearToYearRest <- yearToYearRatesRest |>
  mutate(Region = 'Other')
```


# Combine Three Regions into Final Plot

```{r}
fullYearToYear <- rbind(yearToYearUS, yearToYearMLC, yearToYearRest) 

fullYearToYear <- fullYearToYear |>
  mutate(Region = factor(Region, levels = c('Mainland China', 'United States', 'Other')))
```


```{r}
ggplot(fullYearToYear, aes(x = Year, y = ImproveRate, colour = Region)) +
  geom_point(size = 2) +
  geom_line(size = 0.8, aes(linetype = Region)) +
  ggtitle('Ratio of Universities with Annual Increase in Publications') +
  xlab('Year') +
  ylab('% Universities with Increase') +
  expand_limits(y = 0) +
  scale_x_continuous(breaks = 2014:2023) +
  theme(plot.title = element_text(size = 18,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 12,
                                   color = '#4b4b4b',
                                   face = 'bold')) +
  theme(axis.title.x = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 14,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(legend.title = element_blank()) +
  theme(plot.caption = element_text(size = 12,
                                    color = '#4b4b4b')) +
  labs(caption = 'Other Nations: UK, Germany, France, Japan, South Korea') +
  scale_colour_manual(values = c('Other' = '#5B92E5',
                                 'Mainland China' = '#CC0000',
                                 'United States' = '#0A3161')) +
  theme(legend.position = 'top')

ggsave('Ratio of Universities with Annual Increase in Publications.png', width = 8, height = 4, units = 'in', dpi = 300)
```



# Global Research Funding


```{r}
sector <- read_excel('Research Expenditure as % of GDP.xlsx', skip = 3)

sector <- sector |>
  filter(Year >= 2002 & Year <= 2021) |>
  mutate(China = as.numeric(China),
         `European Union` = as.numeric(`European Union`),
         Year = as.numeric(Year)) |>
  mutate(lagJapan = Japan - lag(Japan),
         lagUS = `United States` - lag(`United States`),
         lagChina = China - lag(China),
         lagEU = `European Union` - lag(`European Union`))
```


```{r}
longerSector <- sector |>
  select(Year, lagJapan, lagUS, lagChina, lagEU) |>
  pivot_longer(cols = c('lagJapan', 'lagUS', 'lagChina', 'lagEU'),
               names_to = 'lagNation',
               values_to = 'Spending_Diff_GDP') |>
  mutate(Nation = case_when(
    lagNation == 'lagJapan' ~ 'Japan',
    lagNation == 'lagUS' ~ 'United States',
    lagNation == 'lagChina' ~ 'China',
    lagNation == 'lagEU' ~ 'European Union'
  )) |>
  select(Year, Nation, Spending_Diff_GDP) |>
  filter(is.na(Spending_Diff_GDP) == FALSE) |>
  mutate(Nation = factor(Nation, levels = c('United States', 'China', 'European Union', 'Japan')))
```


```{r}
ggplot(longerSector, aes(x = Year, y = Spending_Diff_GDP, colour = Nation)) +
  geom_line(aes(linetype = Nation)) +
  ggtitle('Yearly Changes in R&D Spending') +
  xlab('Year') +
  ylab('Spending Change (% of GDP)') +
  geom_hline(yintercept = 0) +
  theme(plot.title = element_text(size = 18,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 12,
                                   color = '#4b4b4b',
                                   face = 'bold')) +
  theme(axis.title.x = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 14,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(legend.title = element_blank()) +
  theme(plot.caption = element_text(size = 10,
                                    color = '#4b4b4b')) +
  scale_colour_manual(values = c('European Union' = '#5ba45b',
                                 'United States' = '#0a3161',
                                 'Japan' = '#c1328e',
                                 'China' = '#cc0000')) +
  theme(legend.position = 'top')

ggsave('Yearly Changes in R&D Spending.png', width = 8, height = 4, units = 'in', dpi = 300)
```


# Global Funding by Sector


```{r}
sector3 <- read_excel('Full National Research Funding by Year.xlsx')
```



```{r}
longerSector3 <- sector3 |>
  filter(Year >= 2003 & Year != 2022) |>
  select(Year, Nation, Enterprise) |>
  mutate(Enterprise = as.numeric(Enterprise),
         Nation = factor(Nation, levels = c('United States', 'China', 'European Union', 'Japan'))) 
```



```{r}
ggplot(longerSector3, aes(x = Year, y = Enterprise, colour = Nation)) +
  geom_line(aes(linetype = Nation)) +
  ggtitle('% of Research Spending from Enterprise') +
  xlab('Year') +
  ylab('% of Total Spending') +
  theme(plot.title = element_text(size = 18,
                                  color = '#4b4b4b',
                                  face = 'bold')) +
  theme(legend.text = element_text(size = 12,
                                   color = '#4b4b4b',
                                   face = 'bold')) +
  theme(axis.title.x = element_text(size = 16,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.title.y = element_text(size = 14,
                                    color = '#4b4b4b',
                                    face = 'bold')) +
  theme(axis.text.x = element_text(color = '#4b4b4b',
                                   face = 'bold')) +
  theme(legend.title = element_blank()) +
  theme(plot.caption = element_text(size = 10,
                                    color = '#4b4b4b')) +
  scale_colour_manual(values = c('European Union' = '#5ba45b',
                                 'United States' = '#0a3161',
                                 'Japan' = '#c1328e',
                                 'China' = '#cc0000')) +
  theme(legend.position = 'top')

ggsave('Research Spending from Enterprise.png', width = 8, height = 4, units = 'in', dpi = 300)
```


